---
title: "Lab 13: Inference for Several Means"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(forcats)
library(ggplot2)
library(dplyr)
library(smodels)
theme_set(theme_minimal())
```


## Burrito synergy in SoCal

Today we will look at a dataset of reviews of burritos in southern
California. This is a data set collected by a group of college friends who
live in the greater San Diego area.

```{r}
burrito <- read_csv("https://statsmaths.github.io/stat_data/burrito.csv")
```

The available variables in the data are:

- location: the name of the restaurant
- cost: total cost for the burrito
- yelp: the average Yelp review score
- google: the average Google review score
- chips_included: equals 1 if chips are included with the burrito
- hunger: score from 1 to 5 on how much the burrito filled up the reviewer
- tortilla: rating from reviewer; 1 (terrible) to 5 (awesome)
- temp: rating from reviewer; 1 (terrible) to 5 (awesome)
- meat: rating from reviewer; 1 (terrible) to 5 (awesome)
- fillings: rating from reviewer; 1 (terrible) to 5 (awesome)
- meat_filling: rating from reviewer; 1 (terrible) to 5 (awesome)
- uniformity: rating from reviewer; 1 (terrible) to 5 (awesome)
- salsa: rating from reviewer; 1 (terrible) to 5 (awesome)
- synergy: rating from reviewer; 1 (terrible) to 5 (awesome)
- wrap: rating from reviewer; 1 (terrible) to 5 (awesome)
- overall: rating from reviewer; 1 (terrible) to 5 (awesome)
- lat: latitude (in degrees North) of the taco restaurant
- lon: longitude (in degrees East) of the taco restaurant

Fit a linear regression predicting the average yelp score of locations in this
dataset and look at the model using `reg_table`:

```{r}
model <- lm_basic(yelp ~ 1, data = burrito)
reg_table(model, level = 0.95)
```

The average Yelp score of all restaurants in this area is just 3.7; looking
at the confidence interval from the model does it seem likely that burrito
locations have a higher Yelp rating than locations in general, or is this
just noise in the data?

**Answer**: No, it seems like they intentionally selected restaurants with
good yelp scores.

The regression model confidence interval requires that the data are sampled
independently from the larger population. Why might this dataset not hold to
this assumption?

**Answer**: They likely only selected good restaurants or those that were close
to where they lived.

Now fit a linear regression that predicts the yelp score as a function of
whether the burrito includes chips.

```{r}
model <- lm_basic(yelp ~ chips_included, data=burrito)
reg_table(model, level = 0.95)
```

Describe what the chips coefficient in the previous model means in words:

**Answer**: Its the additional amount that you would expect a restaurant
that includes chips with their burritos to have as a yelp score.

Is the slope coefficient statistically significant from zero (in other words,
is zero in the confidence interval)?

**Answer**: No, it runs from -0.20652 to 0.320 (a negative to a positive value).

Describe this in terms of your answers above.

**Answer**: There does not seem to be a statistically significant difference in the
Yelp score based on whether chips are included with the burrito.

The word *synergy* can be defined as:

> the interaction or cooperation of two or more organizations, substances,
> or other agents to produce a combined effect greater than the sum of
> their separate effects.

This is not something I would have thought of when considering tacos, but
let's see how synergy effected the scores of both the reviewers as well as
Google and Yelp users in general.

First, I'll add a variable called high_synergy defined as whether the synergy
score is greater than 3.5.

```{r}
burrito$high_synergy <- (burrito$synergy > 3.5)
```

Fit a regression predicting the Yelp score as a function of the
variable `high_synergy`.

```{r}
model <- lm_basic(yelp ~ high_synergy, data = burrito)
reg_table(model, level = 0.95)
```

Is there strong evidence that Yelp scores are higher for high synergy burrito
restaurants?

**Answer**: No, again the confidence interval extends from a negative value to
a positive one.

Now fit a regression predicting the overall score as a function of the
variable high_synergy.

```{r}
model <- lm_basic(overall ~ high_synergy, data = burrito)
reg_table(model, level = 0.95)
```

Is there evidence that high synergy burrito locations have a higher overall
score than low synergy burrito locations?

**Answer**: Yes! The confidence interval runs from 0.87 to 1.465.

Using the model from the previous question, what does the model predict
will be the overall score of a location with low synergy?

**Answer**: 2.69.

What does the model predict will be the overall score of a location with
high synergy?

**Answer**: 2.69 + 1.1678 = `r 2.69 + 1.1678`.

Finally, fit a regression model that predicts the overall score as a function
of the variable `synergy` coded as a factor. That is, use
`overall ~ factor(synergy)` in the formula. We are doing this so that each
value of the synergy score (1, 2, 3, 4, and 5) are treated as a category rather
than a continuous variable.

```{r}
model <- lm_basic(overall ~ factor(synergy), data = burrito)
reg_table(model, level = 0.95)
```

What does the model predict the overall score for a restaurant with a
synergy score of 3 will be?

**Answer**: 2.5 + 0.6917 = `r 2.5 + 0.6917`

Finally, draw a plot that corresponds to the model you just produced for the
synergy score. Hint: You'll need the `geom_confint` layer.

```{r}
ggplot(burrito, aes(factor(synergy), overall)) +
  geom_confint()
```


