---
title: "Lab 03: Exploratory Data Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
theme_set(theme_minimal())
```

The lab today lets you see a few more things that we can do in R with the
Arbuthnot dataset. Again, we will cover the specifics in a few weeks. The
point is to become familiar with the R interface so that once we get to
formal graphics the code looks less overwhelming.

We need to read in the Arbuthnot dataset once again:

```{r}
arbuthnot <- read_csv("https://statsmaths.github.io/stat_data/arbuthnot.csv")
```

Click on the data in the top right hand pane. This will open an Excel
like view of the dataset. Describe what the variable `head_of_state` most
likely means:

**Answer**:

Another way to look at the data is by typing its name and running the
dataset name verbatim. Run the command `arbuthnot` below:

```{r}
arbuthnot
```

You might also have noticed the row of three letter abbreviations under
the column names. These describe the type of each variable:

- `int` stands for integers.
- `dbl` stands for doubles, or real numbers.
- `chr` stands for character vectors, or strings.

The types of graphics and data manipulation we can do with a given
variable is highly determined by the variable data types.

Explain in words why the variables `boys` and `girls` are interpreted as
integers.

**Answer**:

Create a box plot of the heads of state:

```{r}
ggplot(births, aes(head_of_state)) +
  geom_line()
```

Who was the longest serving head of state during the time period of this
data set?

**Answer**:

How are the heads of state arranged be default?

**Answer**:

We can add color to the plot from the last Lab to combine the head of state
information with the year and total number of births: 

```{r}
ggplot(births, aes(year, total)) +
  geom_line(aes(color = head_of_state))
```

Under which heads of state was the number of girls born consistently low?

**Answer**:

## Submission

Once you fill in your answers above, save the file and submit using GitHub just
as you did with the first assignment.
