---
title: "Lab 03: Exploratory Data Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
theme_set(theme_minimal())
```

This lab involves just a few short exercises to continue getting you familiar
with R. Again, we will cover all of the details in full throughout the semester.

Start by reading in the `storms` dataset. This gives readings from historical
Atlantic hurricanes from 2000-2015:

```{r, message=FALSE}
storms <- read_csv("https://statsmaths.github.io/stat_data/storms2.csv")
```

We can draw a bar plot to see the number of storms each year:

```{r}
ggplot(storms, aes(year)) +
  geom_bar()
```

What year seems to have the most readings and which seems to have the fewest?

**Answer**:

Looking at the data, why can be not assume that the year with the highest counts
had the highest number of storms?

**Answer**:

The follow plot shows the relationship between storm winds and latitude (how far
north the center of the storm is):

```{r}
ggplot(storms, aes(lat, wind)) +
   geom_point(aes(color = status))
```

Describe a relationship you see in the plot.

**Answer**:

In R we can construct new datasets from our original inputs. Here, we filter out
just a single storm, Kate from 2015.

```{r}
sandy <- filter(storms, name == "Sandy", year == 2012)
```

We can then plot the storm trajectory as a function of latitude and longitude:

```{r}
ggplot(sandy, aes(long, lat)) +
  geom_point(aes(color = wind)) +
  scale_color_viridis()
```

At what latitude was the storm's measured wind speeds the highest?

**Answer**:

## Submission

Once you fill in your answers above, save the file and submit using GitHub just
as you did with the first assignment.
