---
title: "Lab 07: Grammar of Graphics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(smodels)
theme_set(theme_minimal())
```

## Tea Reviews

Next, we will take another look at a dataset of tea reviews that I used in
a previous lecture:

```{r}
tea <- read_csv("https://statsmaths.github.io/stat_data/tea.csv")
```

With the following variables:

- name: the full name of the tea
- type: the type of tea. One of:
    - black
    - chai
    - decaf
    - flavors
    - green
    - herbal
    - masters
    - matcha
    - oolong
    - pu_erh
    - rooibos
    - white
- score: user rated score; from 0 to 100
- price: estimated price of one cup of tea in cents
- num_reviews: total number of online reviews

Draw a scatter plot with num_reviews (x-axis) against score (y-axis):

```{r}

```

Now add a best fit line to the scatter plot:

```{r}

```


Does the score tend to increase, decrease, or remain the same as the number
of reviews increases?

**Answer**:

Create a text plot with score (x-axis) against price (y-axis). What is the 
most expensive tea in the data? 

**Answer**:

Which tea has the lowest score? Does it have a high price per cup?

**Answer**:

Create a scatter plot of with num_reviews (x-axis) against score (y-axis) and
a facet by tea type:

```{r}

```

Repeat the above plot but allow the scales to be free:


```{r}

```

Which of the two facet plots do you find more readable and why? (Hint: there is
not a right answer here)

**Answer**:

