---
title: "Exam III: Graphics and Filtering"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(dplyr)
library(forcats)
library(smodels)
theme_set(theme_minimal())
```

## Instructions

This exam is the same format as the labs we have been completing in class. Just
fill in R code where required and answer the questions where you see the ANSWER
prompt. The only difference is that you must work on the exam external help. You
may consult the class notes or look up help online, but may not discuss with
classmates or directly ask questions of others. If you have any questions about
this policy, please ask me first before using a resource.

There are five sections Each one requires you to build a regression model with
`lm_basic`, print out the results, and answer a short question. Each section also
requires you to produce one plot. The answers do not require justification and
(this time) you do not need to label the plot axes.

The completed Rmarkdown file must be submitted by 5pm on November 19th (Monday)
in the 'exams' directory on your GitHub repository. While I suggest that you
knitand produce an HTML version of the exam (it is a good way to check that your
code runs correctly), it is not required and you do not need to submit this file.
If you have trouble with the upload, please email me the Rmd file and provide
a description of the problem you encountered.

Good luck!

## Weather in NYC

The dataset for this exam is nearly the exact same as that from the previous exam:
a single year of observed weather data from New York City. A few of the variables
are slightly different. Read in the dataset with this command (it also reorders
one variable to make the plots look nicer):

```{r}
weather <- read_csv("https://statsmaths.github.io/stat_data/weather-nyc-2.csv")
weather$month <- fct_inorder(weather$month)
```

Here is a data dictionary for the variables:

- **date**: 	               the date of the weather record, formatted YYYY-MM-DD
- **actual_mean_temp**: 	   the measured average temperature for that day (celsius)
- **actual_min_temp**: 	     the measured minimum temperature for that day (celsius)
- **actual_max_temp**: 	     the measured maximum temperature for that day (celsius)
- **average_min_temp**: 	   the average minimum temperature on that day since 1880 (celsius)
- **average_max_temp**:      the average maximum temperature on that day since 1880 (celsius)
- **record_min_temp**: 	     the lowest ever temperature on that day since 1880 (celsius)
- **record_max_temp**: 	     the highest ever temperature on that day since 1880 (celsius)
- **record_min_temp_year**:  the year that the lowest ever temperature occurred
- **record_max_temp_year**:  the year that the highest ever temperature occurred
- **actual_precipitation**:  the measured amount of rain or snow for that day (cm)
- **average_precipitation**: the average amount of rain or snow on that day since 1880 (cm)
- **record_precipitation**:  the highest amount of rain or snow on that day since 1880 (cm)
- **record_precipitation**:  the highest amount of rain or snow on that day since 1880 (cm)
- **month**:                 character description of the month
- **description**:           character description of the weather type; one of: "rain", "snow", or "dry"

If other questions about what these variables mean arise, please let me know.

## 1. Mean of the actual mean temperature

Draw a bar plot for the variable `actual_mean_temp`:

```{r}

```

Build a model for the average of the variable `actual_mean_temp` and
produce a 95% confidence interval.

```{r}

```

Give the 95% confidence interval for the mean of the variable
`actual_mean_temp`:

**ANSWER**:

## 2. Actual mean temperature

Draw a plot using `geom_confint` with a description of the weather (see the
variable `description`) on the x-axis and the `actual_max_temp` on the y-axis.

```{r}

```

Build the regression model corresponding to the plot above and produce a 95%
confidence interval.

```{r}

```

Is there a statistically significant difference between the `actual_max_temp`
on rainy days and dry days?

**ANSWER**:

## 3. Mean versus minimum

Draw a scatter plot with the `actual_mean_temp` on the x-axis and `actual_min_temp`
on the y-axis. Include a best fit line.

```{r}

```

Fit a regression model corresponding the plot above (i.e., predict the variable
`actual_min_temp` as a function of `actual_mean_temp`):

```{r}

```

What does the model predict will be the minimum tempurature on a day
where the average temperature is 20 degrees Celsius.

**ANSWER**:

## 4. Maximum temperature by month

Draw a boxplot with month on the x-axis and `actual_max_temp` on the y-axis:

```{r}

```

Fit a model corresponding the plot above:

```{r}

```

The baseline in the model should be July. What months do NOT
have a statistically significant difference in `actual_max_temp`
compared to July.

**ANSWER**:

## 5. Record setting temperature by month

Draw a plot with `geom_confint` using month on the x-axis and the
`record_max_temp_year` on the y-axis.

```{r}

```

Fit a model corresponding to the plot and produce a 95% confidence interval.

```{r}

```

What range of years does your model predict the average year of
the record max temperature will be in April?

**ANSWER**:




