---
title: "Lab 06: Tidy Data"
output: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(smodels)
theme_set(theme_minimal())
```

To start, create a new dataset with two variables:

- **cuisine**: one row for each of the restaurant types in the class dataset: 
    - "American"
    - "Chinese"
    - "Dessert"
    - "Fast Food" (including fast Mexican such as Chipotle)
    - "Indian"
    - "Italian"
    - "Japanese" (including sushi)
    - "Korean"
    - "Mexican"
    - "Pizza"
    - "Thai"
    - "Vietnamese"
    - "Other"
- **score**: your personal rating of this cuisine type on a scale from 1 (hate
it) to 10 (love it)

Store, download, and save this as a file called `cuisine_rating.csv`. 

# Join tidy data

Now read in the dataset `class_restaurants_fixed.csv` into R:

```{r}
class <- read_csv("class_restaurants_fixed.csv")
```

As well as the new dataset you created:

```{r}
rating <- read_csv("cuisine_rating.csv")
```

Now, use the `left_join` function to join the class dataset (first entry) to 
the rating dataset (second entry). Save the result as a dataset named
`class_new`. (Hint: see the lecture notes for help with this)

```{r}

```

Run the following code to produce a graphic of how each student's picks 
correspond to your ratings. We will talk more about the specifics in a few
weeks.

```{r}
ggplot(class_new, aes(student_name, rating)) +
    geom_mean() +
    coord_flip() +
    xlab("Student Name") + 
    ylab("Average Ranking")
```

Is the highest average score your own? If not, how many students have a higher
ranking for your preferences than you do?

**Answer**:

## Submission

Remember to submit your dataset `cuisine_rating.csv` as well as this completed
file.
