---
title: "Lab 02: Introduction to R and GitHub"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
theme_set(theme_minimal())
```

This second lab, due before the third class meeting, assumes that you have
already installed the packages described in the first lab. You **must** run
the block of code above this text before running anything else. It loads
packages that is used by the rest of the script.

## A short example

### Import and view the data

The next step is to load a dataset into R. Next week will be spent
talking about how to structure our own data; for today, we will work with some
data that I have previously prepared:

```{r, message = FALSE}
births <- read_csv("https://statsmaths.github.io/stat_data/arbuthnot.csv")
```

Here, we are using the **function** `read_csv` to read in a dataset on my
website. The `<-` symbol has saved this dataset as an **object** called
`births`. Notice that the dataset appears in the environment pane in the upper
right-hand corner of RStudio.

The dataset here shows the number of children born in London on an annual
basis, separated by their sex. Interactively in RStudio, you can see the data
as a table by clicking on the table in the upper right-hand corner.

What years are included in the study?

**Answer**:

Where/how do you think this data may have been collected?

**Answer**:

### Plots

Now, let's visualize the dataset by constructing several different plots. We
will learn later how the plotting mechanism actually works. Today just run the
code and enjoy.

```{r}
ggplot(births, aes(year, total)) +
  geom_line()
```

Approximately how many children were born in London in 1701?

**Answer**:

What is one change you'd like to make to the way R has constructed the
plot?

**Answer**:

## Submission

Once you fill in your answers above, save the file and submit using GitHub just
as you did with the first assignment.
