---
title: "Lab 02: Introduction to R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
theme_set(theme_minimal())
```

This second lab, due before the third class meeting, assumes that you have
already installed the packages described in the first lab. You **must** run
the block of code above this text before running anything else. It loads
packages that is used by the rest of the script.

## A short example

### Import and view the data

The next step is to load a dataset into R. Next week will be spent
talking about how to structure our own data; for today, we will work with some
data that I have previously prepared:

```{r, message = FALSE}
births <- read_csv("https://statsmaths.github.io/stat_data/arbuthnot.csv")
```

Here, we are using the **function** `read_csv` to read in a dataset on my
website. The `<-` symbol has saved this dataset as an **object** called
`births`. Notice that the dataset appears in the environment pane in the upper
right-hand corner of RStudio.

The dataset here shows the number of children born in London on an annual
basis, separated by their sex. Interactively in RStudio, you can see the data
as a table by clicking on the table in the upper right-hand corner.

What years are included in the study?

**Answer**:

Where/how do you think this data may have been collected?

**Answer**:

### Plots

Now, let's visualize the dataset by constructing several different plots. We
will learn later how the plotting mechanism actually works. Today just run the
code and enjoy.

```{r}
ggplot(births, aes(year, total)) +
  geom_line()
```

Approximately how many children were born in London in 1701?

**Answer**:

What is one change you'd like to make to the way R has constructed the
plot?

**Answer**:


Click on the data in the top right hand pane. This will open an Excel
like view of the dataset. Describe what the variable `head_of_state` most
likely means:

**Answer**:

Another way to look at the data is by typing its name and running the
dataset name verbatim. Run the command `arbuthnot` below:

```{r}
arbuthnot
```

### Variables

You might also have noticed the row of three letter abbreviations under
the column names. These describe the type of each variable:

- `int` stands for integers.
- `dbl` stands for doubles, or real numbers.
- `chr` stands for character vectors, or strings.

The types of graphics and data manipulation we can do with a given
variable is highly determined by the variable data types.

Explain in words why the variables `boys` and `girls` are interpreted as
integers.

**Answer**:

Create a box plot of the heads of state:

```{r}
ggplot(births, aes(head_of_state)) +
  geom_line()
```

Who was the longest serving head of state during the time period of this
data set?

**Answer**:

How are the heads of state arranged be default?

**Answer**:

We can add color to the plot from the last Lab to combine the head of state
information with the year and total number of births:

```{r}
ggplot(births, aes(year, total)) +
  geom_line(aes(color = head_of_state))
```

Under which heads of state was the number of girls born consistently low?

**Answer**:

### Critical thinking

The Arbuthnot data set refers to Dr. John Arbuthnot,
an 18th century physician, writer, and mathematician. He gathered the
baptism records for children born in London for every year from 1629 to
1710. He was interested in studying what we would now call the **secondary
sex ratio**, the ratio of males to females in a population at birth. This
would later be a major element of study of Ronald Fisher, one of the most
well-known, early pioneering statisticians.

Why would John Arbuthnot be using baptism records to study his question of
interest? (Note: I'll ask you a lot of "thought" questions like this that
require critical thinking rather than coding or numerical analysis):

**Answer**:

## Present Day Data

Now, for practice, read in the following dataset with the same
information for the present day:

```{r}
present <- read_csv("https://statsmaths.github.io/stat_data/present.csv")
```

What years are included in this data set?

**Answer**:

How do these counts compare to Arbuthnot's? Are they of a similar
magnitude?

**Answer**:

Make a plot that displays the proportion of boys born over time.

```{r}

```

What do you see?

**Answer**:

In what year did we see the highest total number of births in the U.S.?
Note: You'll need another plot.

```{r}

```

**Answer**:

Reconstruct the line plot that is colored by the current head of state.

```{r}

```

Do you see any patterns related to particular presidencies? What benefit(s)
does including this information add to the plot?

# Answer:


## Submission

Once you fill in your answers above, save the file and submit using GitHub just
as you did with the first assignment.
