---
title: "Lab 08: Aesthetic Mappings"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(ggrepel)
library(dplyr)
library(smodels)
theme_set(theme_minimal())
```

## Miles Per Gallon

Make sure to start by running the setup chunk above to load the required packages.
Then, read in the mpg dataset. There is one row for each particular type of car,
with information about the fuel efficiency and other metadata.

```{r, message=FALSE}
mpg <- read_csv("https://statsmaths.github.io/stat_data/mpg.csv")
```

The variable `displ` gives the size of the engine in litres and `cty` the reported
miles per gallon of the car while driving in stop-and-go city traffic. Likewise,
`hwy` is the miles per gallon for a car on the highway.

Start by making a scatter plot (i.e., points) of engine size on the x-axis and the
highway fuel efficiency on the y-axis.

```{r}

```

Verify that the pattern in this plot makes sense.

Next, modify the plot so that the color of the points show the class of the vehicle.

```{r}

```

Identify a few different classes of vehicles and verify that they appear where
you would expect on the plot.

Now, make all of the points in the plot twice as big and color them the color
green.

```{r}

```

Next, create two scatter plots at once by adding together `geom_point` layers
where one layer uses `hwy` as the y-axis and the other users `cty` as the
y-axis (yes, you can override the y aesthetic just like any other).

```{r}

```


In the previous plot, it is impossible to distinguish between the points that
are of the highway fuel efficiencies values and the city fuel efficiencies.
Change this by making the city fuel efficiencies colored in red.

```{r}

```

The default y-axis label is no longer correct because it actually measures two
different fuel efficiencies. Add the layer `ylab("Miles Per Gallon")` to the
plot to fix this:

```{r}

```

Finally, do the same with the `xlab` and `ggtitle` functions to add a better
x-axis and title.

```{r}

```

## Democratic Primary 2016

Now, load data from the 2016 Democratic Primary elections. The data is given
at the county level (this is the **unit of analysis**).

```{r}
primary <- read_csv("https://statsmaths.github.io/stat_data/primary2016.csv")
```

Start by drawing a scatter plot of latitude and longitude (it is up to you
to determine which goes on the x and y axes):

```{r}

```

Next, color the points based on the variable `division`.

```{r}

```

Then, color the points based on the variable `prop_hillary` (the proportion of
votes Hillary Clinton received).

```{r}

```

Notice any interesting patterns here? Try loading the **viridis** package:

```{r}
library(viridis)
```

And add `scale_color_viridis()` to the plot:

```{r}

```

It should look much more readable. Do you notice any patterns now?

## Project I data

Now, put the three csv files that you created for Project I into the lab folder.
Make sure they are named `activities.csv`, `places.csv`, and `hourly.csv`. We
will work with these a bit over the next few labs.

Read in the hourly and places dataset:

```{r}
hourly <- read_csv("hourly.csv")
places <- read_csv("places.csv")
```

Now, make use of `left_join` to combine the two datasets (see lab06
for help if you forgot how to do this) and overwrite the dataset
named hourly:

```{r}

```

Create a plot of longitude and latitude using a `geom_point` layer
(you'll want longitude on the x-axis):

```{r}

```

Now, repeat the plot and add a `geom_path` layer. This connects the dots in
the order they are given in the dataset:

```{r}

```

In order for us to know what the data points are, add another `geom_text`
label with a label equal to the location name:

```{r}

```

Finally, make a bar plot or histogram, whichever is most appropriate, for
the variable that you added to the hourly dataset.

```{r}

```


