---
title: "Lab 07: Grammar of Graphics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(smodels)
theme_set(theme_minimal())
```

## Tea Reviews

Here, we will take look at a dataset of tea reviews from Adagio Teas:

```{r}
tea <- read_csv("https://statsmaths.github.io/stat_data/tea.csv")
```

With the following variables:

- name: the full name of the tea
- type: the type of tea. One of:
    - black
    - chai
    - decaf
    - flavors
    - green
    - herbal
    - masters
    - matcha
    - oolong
    - pu_erh
    - rooibos
    - white
- score: user rated score; from 0 to 100
- price: estimated price of one cup of tea in cents
- num_reviews: total number of online reviews

Draw a scatter plot with num_reviews (x-axis) against score (y-axis):

```{r}

```

Now add a best fit line to the scatter plot:

```{r}

```


Does the score tend to increase, decrease, or remain the same as the number
of reviews increases?

**Answer**:

Create a text plot with score (x-axis) against price (y-axis) using the tea
name as a label. What is the most expensive tea in the data?

**Answer**:

Which tea has the lowest score? Does it have a high price per cup?

**Answer**:

Create a scatter plot of with num_reviews (x-axis) against score (y-axis) and
a facet by tea type:

```{r}

```

Repeat the above plot but allow the scales to be float freely:


```{r}

```

Which of the two facet plots do you find more readable and why? (Hint: there is
not a right answer here)

**Answer**:

## Class dataset

Now, read in the class dataset once again (it should be in your labs folder already).

```{r}
class <- read_csv("class_restaurants_fixed.csv")
```

Make a text plot of the frequency of the restaurant against its price, with the name
of the restaurant as the label.

```{r}

```

Do you notice any interesting patterns in the plot?

**Answer:**

Now, in the code below, add these new layers to the plot you just made:
`scale_x_log10()` and `scale_y_log10()`.

```{r}

```

How do these change the plot?

Now, create a plot that shows the mean price of the restaurants by cuisine:

```{r}

```

And similarly, show the mean frequency of visits by cuisine:

```{r}

```

Describe something you find interesting in these two plots in a couple of sentences:

**Answer**:









