---
title: "Lab 05: Data Dictionary"
output: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
theme_set(theme_minimal())
```

Here is a template for creating a data dictionary in RMarkdown:

- **student_name**: a character variable giving each student's given (i.e.,
what we would call "First Name" in English) or preferred name
- **name**: a character variable giving the full proper name of the restaurant
- **location**: a character variable giving the location of the restaurant
as "City, State", with state represented using the two-character state postal
code
- **cuisine**: a categorical variable describing the primary cuisine type of
the restaurant. Possible options are:
    - "American"
    - "Chinese"
    - "Dessert"
    - "Fast Food" (including fast Mexican such as Chipotle)
    - "Indian"
    - "Italian"
    - "Japanese" (including sushi)
    - "Korean"
    - "Mexican"
    - "Pizza"
    - "Thai"
    - "Vietnamese"
    - "Other"
- **fav_dish**: a character variable describing student's favorite dish
- **cost_per_person**: numeric variable describing approximate total amount in
dollars, after tax in tip, that the student typically spends per person when
visiting the restaurant
- **yearly_visits**: numeric number of times student typically visits the
restaurant in a given 12-month period. Use only whole numbers. If less than 1,
round down to zero.
- **last_visit**: character variable describing the last time the student
visited the restaurant. Format as "YYYY-MM" with the four digit year and two
digit month.

Use the same format for your data dictionary.

## Questionnaire Dictionary

Create a data dictionary for the questions that you put on the board here in
the RMarkdown file:



## Dataset

Construct 6 fake answers to the questions you posed in the questionnaire as a
CSV file. Download the file, name it `questions.csv`, and put the file in the
same location as this file.

Now read the dataset into R:

```{r}
quest <- read_csv("questions.csv")
```

Modifying the code from one of the previous labs, create two plots of the data:

```{r}

```

```{r}

```

## Class data

Download a new version of the class dataset and name it
`class_restaurants_fixed.csv`. Read in the dataset into R:

```{r}
class <- read_csv("class_restaurants_fixed.csv")
```

Reproduce a bar plot of cuisine types.

```{r}

```

How does this compare to the version you had from the last lab?

**Answer**:


Reproduce a scatter plot of year versus price:

```{r}

```

How does this compare to the version you had from the last lab?

**Answer**:

## Submission

Remember to submit your datasets as well as this completed file.
