---
title: "Lab 04: Data Basics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
theme_set(theme_minimal())
```

This lab assumes that you have downloaded and renamed a file called
`my_restaurants.csv` and placed it in the same location as this
RMarkdown file.

## Reading in a local file

You can read the csv file in with the following code:

```{r, eval = FALSE}
mine <- read_csv("my_restaurants.csv")
```

Notice that I have called it something short but memorable (`mine`)
to make it easier to write code about the dataset. Open the file with the
data viewer (open right hand corner) and check that it matches what you
created.

### Simple plotting, again

Recall that we can create plots in R. Specifically, use something like this
to get a bar plot of the cuisine types:

```{r}
ggplot(mine, aes(cuisine)) +
  geom_bar()
```

Copy and paste the code above in the chunk below but change the variable to
something else and note what happens:

```{r}

```

For a scatter plot of how often you visit each year and the average cost, use
this:

```{r}
ggplot(mine, aes(year, cost)) +
  geom_point()
```

Similarly, copy the scatter plot code below and see what happens if you use a
difference pair of variables:

```{r}

```

We will now return briefly the class notes.

### Plotting, once again

Now, after downloading the entire class dataset, read in this file as a data
set named `class` (Hint: copy and modify the code from above):

```{r}

```

Repeat the bar plot of cuisine for the new dataset:

```{r}

```

And repeat the scatter plot of year and cost:

```{r}

```

As you explore the dataset, are there any interesting patterns or outliers
in the data?

**Answer**:

What benefit of writing analysis as code is illustrated well in the lab
today?

**Answer**:

## Submission

When submitting this lab, make sure to also upload the csv files
`my_restaurants.csv` and `class_restaurants.csv` in order to receive credit for
the assignment. Generally if you create a dataset as part of a lab, you should
also upload the data itself.
