---
title: "Lab 10: Filtering Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(ggmap)
library(dplyr)
library(smodels)
theme_set(theme_minimal())
```

## Filtering the class dataset

To start, read in your project datasets and join the places information to the
hourly data.

```{r}
hourly <- read_csv("hourly.csv")
places <- read_csv("places.csv")
activities <- read_csv("activities.csv")
hourly <- left_join(hourly, places)
hourly <- left_join(hourly, activities)
```

It's possible that in converting your data into excel or Google Sheets that the
time variable became too messy for R to read correctly. This line should fix 
things:

```{r}
start <- as.POSIXct("2018-09-17 00:00")
end <- start + as.difftime(7, units="days")
hourly$hour <- seq(from=start, by=60*60, to=end)[seq_len(nrow(hourly))]
```

Now, these create three filtered datasets from `hourly`:

- `hourly_week`: select only data from Monday at midnight through Friday at 5pm
- `hourly_tornado`: select only data from Monday at 3pm until Monday at 6pm
- `hourly_fav`: select whatever your favorite 1-3 hours of the entire week were

In the code chunk below (you can do this all in the same code block):

```{r}

```

Then, conctruct a plot with `hour` on the x-axis and `score` on the y-axis using
a `geom_line` layer. Then, add an extra point layer that shows the points in
`hourly_tornado` in red. Finally, add a text annotation that tells readers of the
plot what happened during the red period.

```{r}

```

## Pick a dataset

For the remainder of this lab, you choice of three datasets to work with.
You can choose either to investigate the daily team ELO ratings in the NBA:

```{r}
nba <- read_csv("https://statsmaths.github.io/stat_data/nba_elo_daily.csv")
```

Metadata from US senator's tweets:

```{r}
tweets <- read_csv("https://statsmaths.github.io/stat_data/senator_tweets_meta.csv")
```

Or swear words given in the movies of Quentin Tarantino:

```{r}
tarantino <- read_csv("https://statsmaths.github.io/stat_data/tarantino.csv")
```

Pick a dataset (feel free to delete the others from the Rmd file if you would
like), and work on the instructions in the next section.

## Instructions

This lab is similar to the last. You'll pick a dataset and then generate an
analysis of that data using data visualizations. The difference here is that
instead of a single plot, I would like you to construct 3-4 plots that
together tell a linear story. Each plot should be separated by a sentence or
two describing what the viewer should take away from the plot. Try to keep the
plots similar in some way; perhaps each simply highlights a different subset
of the data but has the same underlying layers.

Notice that each of the datasets for today are larger than you will probably
be able to use. You will need to filter the data to a particular team, year,
subset of curse words. You may further filter the data to highlight an even
smaller subset of the data within each plot.

## Analysis


