\documentclass[11pt]{article}
\usepackage[top=1.5cm,bottom=2cm,left=2cm,right= 2cm]{geometry}
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}            
\usepackage{multirow}    
\usepackage{multicol}    
\usepackage{changepage}
\usepackage{lscape}
\usepackage{enumitem}
\usepackage{ulem}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancyplain}
\fancyhf{}

\usepackage{xcolor}

\definecolor{oiB}{rgb}{.337,.608,.741}
\definecolor{oiR}{rgb}{.941,.318,.200}
\definecolor{oiG}{rgb}{.298,.447,.114}
\definecolor{oiY}{rgb}{.957,.863,0}

\definecolor{light}{rgb}{.337,.608,.741}
\definecolor{dark}{rgb}{.337,.608,.741}

\usepackage[colorlinks=false,pdfborder={0 0 0},urlcolor= dark,colorlinks=true,linkcolor=black]{hyperref}

\newcommand{\light}[1]{\textcolor{light}{\textbf{#1}}}
\newcommand{\dark}[1]{\textcolor{dark}{#1}}
\newcommand{\gray}[1]{\textcolor{gray}{#1}}


\date{2018-07-01}                                           % Activate to display a given date or no date

%

\begin{document}

{\Large \textcolor{oiB}{
Class 01: Course Introduction
\hfill Learning Objectives}} \\

\textbf{Name:} \underline{\hspace{6cm}} \\

I plan to hand out a sheet similar to this one each day of class listing the
learning objectives for the day. Below the line is where you will answer the
end-of-lecture questions. Make sure to fill in your name as you will be
handing these in for a pass/fail grade during class.

\vspace{0.2cm}

\begin{enumerate}
\renewcommand\labelenumi{\textcolor{light}{\textbf{LO \theenumi.}}}

\item Identify key elements of the course structure from the syllabus. Inquire
about any unclear points or potential concerns.

\item Record dates of exams, due-dates for projects/essays, and location of
resources such as the course website and office hours.

\item Describe at a high-level the three components of the data analysis
pipeline.

\item Install \textbf{R} and \textbf{RStudio} on your laptop computer.
Communicate any difficulty you have with this process.

\end{enumerate}

\noindent\makebox[\linewidth]{\rule{1.1\textwidth}{0.4pt}}



\end{document}
